%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% Editor:
% Furkan Varol
%
% Repository:
% https://github.com/furkanvarol/resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{furkanvarol-resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Furkan}{Varol}{ \urlstyle{same}\href{http://www.furkanvarol.com}{furkanvarol.com} | \href{mailto:furkanvarol@gmail.com}{furkanvarol@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Yildiz Technical Uni.}
\descript{MEng in Computer Engineering}
\location{Started Feb 2016 | Istanbul, Turkey}
\sectionsep

\subsection{Fatih University}
\descript{BS in Computer Engineering}
\location{Grad. June 2014 | Istanbul, Turkey}
\location{CGPA: 3.72 / 4.0}
\sectionsep

\subsection{FH Vorarlberg}
\descript{BS in Computer Science, Erasmus}
\location{Feb - June 2012 | Dornbirn, Austria}
\location{CGPA: 3.67 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/furkanvarol}{\bf furkanvarol} \\
LinkedIn://  \href{https://tr.linkedin.com/in/furkanvarol}{\bf furkanvarol} \\
Twitter://  \href{https://twitter.com/furkan_varol}{\bf @furkan\_varol} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Love:}
Java \textbullet{} Scala \textbullet{} C\# \textbullet{} Python \\
Android \textbullet{} Spring \textbullet{} Play \\
Spark \textbullet{} Hadoop \textbullet{} AWS \\
IntelliJ IDEA \textbullet{} Sublime \textbullet{} ViM \textbullet{} Git \\
RFID \textbullet{} NFC \textbullet{} BLE \textbullet{} Beacon \\
\location{Like:}
C \textbullet{} C++ \textbullet{} Javascript \\
GWT, SmartGWT \textbullet{} .Net \textbullet{} AngularJS \\
Redis \textbullet{} RabbitMQ \textbullet{} SQL \textbullet{} NoSQL \\
\location{Familiar:}
Ruby \textbullet{} iOS \textbullet{} TeX
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certificates
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certificates}

\subsection{Solutions Architect}
\descript{Amazon Web Services}
\location{May 2016 | Associate}
\sectionsep

\subsection{Big Data with Spark}
\descript{edX}
\location{July 2015}
\sectionsep

\subsection{RFID Academy}
\descript{Alien Technology}
\location{June 2014}
\sectionsep

\subsection{High Honor Student}
\descript{Fatih University}
\location{2010 - 2014 | Istanbul, Turkey}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards}
%
%\subsection{High Honor Student}
%\descript{Fatih University}
%\location{2010 - 2014 | Istanbul, Turkey}
%\sectionsep
%
%\subsection{Full Scholarships}
%\descript{Fatih University}
%\location{2009 - 2014 | Istanbul, Turkey}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{References}

Available upon request

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OPEN SOURCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Open Source}
\runsubsection{Spark-ETL}
\descript{| \href{https://github.com/vngrs/spark-etl}{github.com/vngrs/spark-etl}}
\location{August 2016 - Present}
Lead and developed ETL system on top of Apache Spark. Spark-ETL is highly scalable and distributed. It support range of variety of data sources. With them, it can extract data from N sources, transform them and load them to N destinations [Scala, Spark, ...]. 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Zalando SE}
\descript{| Software Developer}
\location{September 2016 - Present | Berlin, Germany}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Maintaining, optimising and improving Zalando's recommendation engine.
\end{tightemize}
\sectionsep

\runsubsection{VNGRS}
\descript{| Software Developer}
\location{June 2015 - August 2016 | Istanbul, Turkey}
\begin{tightemize}
\item Developed a POC for customer segmentation for ad targeting [Java, Spark].
\item Lead and developed data warehouse system (including ETL of production data and visualising it) [Scala, Spark, Redshift, QuickSight].
\item Lead and developed sentiment analysis system to report affects of society sentiment on sales [Scala, Spark, SparkML].
\item Lead and developed customer unification system [Scala, Spark].
\item Maintained, optimised and developed new features on Convertale project.
Convertale is a recommendation engine for e-retailers and news portals works on top of Amazon Web Services [Java, Scala, Spring, Spark, RabbitMQ, Redis, ...].
\end{tightemize}
\sectionsep

\runsubsection{Vendeka}
\descript{| Software Developer}
\location{Dec 2013 - May 2015 | Istanbul, Turkey}
\begin{tightemize}
\item Developed SenseBlue project which uses Apple's iBeacon technology.
SenseBlue allows people to be tracked (with proximity) by smart devices.
Also allows to track objects for cheaper warehouse management solutions - alternative to RFID systems like Akdeniz [Java, Android, Python, Flask, RaspberryPi, ...].
\item Developed new features and fixed bugs on existing Akdeniz project.
Akdeniz is a Smart Warehouse Management System with RFID Technologies [Java, SmartGWT, GWT, .Net, JavaScript, ...].
\end{tightemize}
\sectionsep

\runsubsection{Cyclops Inf. Tech.}
\descript{| Android Developer Intern}
\location{July 2012 - Aug 2012 | Istanbul, Turkey}
\begin{tightemize}
\item Developed and optimised an Android tracking client which is integrated with a working system [Java, Android].
\end{tightemize}
\sectionsep

\runsubsection{Gripati Digital Ent.}
\descript{| Android and iOS Developer Intern}
\location{Nov 2011 - June 2012 | Istanbul, Turkey}
\begin{tightemize}
\item Developed and optimised iPhone and Android game - CorridorFly [JavaScript, Unity 3D, Android].
\end{tightemize}
\sectionsep

\runsubsection{Senior Design Projects}
\descript{| Computer Engineer Student}
\location{Dec 2013 -€“ May 2014 | Istanbul, Turkey}
\begin{tightemize}
\item Lead and developed mobiCard (a NFC loyalty system, works Software as a Service) [Scala, Play, Java, Android, .Net].
\end{tightemize}
\location{Mar 2013 - June 2013 | Dornbirn, Austria}
\begin{tightemize}
\item Lead and developed a mobile chat application (Nearby Chat) which does not require a server (only works on devices in same network - WiFi) [Java, Android].
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}

\runsubsection{Shelf Sort}
\descript{}
\location{Jan 2015 - Present | Istanbul, Turkey}
Worked with \textbf{Assist. Prof. Dr. Ä°hsan Haluk AkÄ±n} to develop a sorting algorithm
based on \textbf{Library Sort} (puts gaps to accelerate \textbf{Insertion Sort}).
Shelf Sort tries to analyze data first and takes advantage of the state for further acceleration.
\sectionsep

\end{minipage}
\end{document}
\documentclass[]{article}
